Kimbee: A Speech Therapy Application For Children

### 2015-01-19 Proposal/proposal.tex
Capitals

    \item Application scaffolding (game structure, menu, options) (week 4)

@@

    \item Simple game screen to connect to speech API for testing (week 4)

@@

    \item Contact therapists and refine project goals / industry need (week 6)

@@

    \item Web Audio API, Microphone capture, Data pipeline in javascript (week 6)

@@

    \item Speech, phoneme recognition in javascript with pocketsphinx.js (week 6)

@@

    \item Progress tracking metrics related to confidence data on child performance (week 8)

@@

    \item Iterate specific progress tracking implementations with therapist feedback (week 8)

@@

    \item More games that utilize javascript speech API defined in the above sections (week 10)

@@

    \item Polish everything, animations, graphics, sound etc. (week 10)

@@

    \item Package up to apps and deliver to app store (week 10)

@@

    \item Write up / Poster (week 11)

>>>>

    \item Application scaffolding (game structure, menu, options) (Week 4)

@@

    \item Simple game screen to connect to speech API for testing (Week 4)

@@

    \item Contact therapists and refine project goals / industry need (Week 6)

@@

    \item Web Audio API, Microphone capture, Data pipeline in javascript (Week 6)

@@

    \item Speech, phoneme recognition in javascript with pocketsphinx.js (Week 6)

@@

    \item Progress tracking metrics related to confidence data on child performance (Week 8)

@@

    \item Iterate specific progress tracking implementations with therapist feedback (Week 8)

@@

    \item More games that utilize javascript speech API defined in the above sections (Week 10)

@@

    \item Polish everything, animations, graphics, sound etc. (Week 10)

@@

    \item Package up to apps and deliver to app store (Week 10)

@@

    \item Write up / Poster (Week 11)
